Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach

### 2016-09-03 MovePattern_IJGI/IJGI_revision/Twitter_MovementPatterns_VisualAnalytics_v2.tex
xxx

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
For instance, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.

Many recent studies have adopted the LBSM data streams to study human mobility patterns.
For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national level), are lacking.
Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.

In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
In particular, the Twitter user mobility patterns measured by the user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
In particular, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.

@@

\section{Mobility patterns in Location Based Social Media data}
\subsection{Geo-located Twitter data for studying large-scale user movements}
To understand detailed mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
However, the data are often limited in spatial scale (e.g. within a specific city or region) with a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively. Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.

Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
Such a dataset can cover relatively large spatial scale~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
However, due to the concerns of infringement on individual privacy, mobile phone call data are not publicly accessible at all.
Even such data were obtained in the mentioned studies, they came from various service providers covering different groups of users.
These issues limit the capability for conducting reproducible scientific findings regarding mobility research, such as validating or extending the existing discoveries.

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
A Big Data scenario emerges when millions social media users constantly posting messages.
In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.

@@

\noindent\emph{\textbf{Definition 2. visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.

In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
The displacement refers to an individual's re-allocation across the geographic space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
It is not equivalent to a ``trip'' took by an individual, for example, even the time interval between two recorded locations is one month, it will still count as a displacement.
By studying the collective displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} and to quantitatively differentiate the mobility patterns from random walks~\cite{brockmann2006scaling}.
On the other hand, radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as fellows.   
\newline

@@

\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, and therefore indicates the individual's spatial coverage, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
When applying the measurement to the study population, it identifies different groups of people in terms of spatial coverage from their corresponding mobility patterns. Note that both displacements and radius of gyrations are measured by ``crow's fly distance'' in this study (i.e., the direct great-circle distance between two recorded locations).
Since these metrics are based on the generated trajectories, by breaking and aggregating the trajectories in multiple spatial scales and temporal ranges, it enables performing multi-scale spatiotemporal analysis on these measurements and studying the corresponding mobility patterns.

\subsection{Multi-level spatiotemporal trajectory aggregation}
An important strategy for visual-analytics methods dealing with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers. 
To be specific, the state boundaries of the continuous United States are treated as the base layer (i.e. level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density.
In our case, the cell size for level i-1 is twice of the size in level i.
Figure~\ref{fig:multilevel} illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
Note that any predefined geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., national-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{./figures/multilevel}
\caption{Hierarchical spatial layers for aggregating movements in different level-of-details}
\label{fig:multilevel}
\end{figure}
\FloatBarrier

@@

In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}. 
The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
Note that different groups of Twitter user may exist in each month. 
It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}, where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).

@@

\begin{figure}[h]
\centering
\includegraphics[width=1.0\linewidth]{./figures/visitation2}
\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors}
\label{fig:visitation}
\end{figure}
\FloatBarrier

As it is mentioned above, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
In this case, we first gathered the displacements from all the collected Twitter users in the continuous United States in year 2014, where those Twitter users with only one geo-located tweet were filtered out. 
To investigate the mobility patterns of individuals, we also derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
Note that both displacements and radius of gyrations were calculated by the direct great-circle distance ($d$) between two consecutively recorded locations in a user's trajectory.

@@

\begin{figure}[h]
\centering
\includegraphics[width=1.0\linewidth]{./figures/displacement}
\caption{(a) The probability distribution of the collective Twitter user displacements P(d) (b) the distance between [100 m, 80 km] is approximated by a double power-law functions (c) The probability distribution of the accumulated displacements of individual Twitter users P(d) (d) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months}
\label{fig:displacement}
\end{figure}
\FloatBarrier

@@

\begin{figure}[h]
\centering
\includegraphics[width=1.0\linewidth]{./figures/gyration2}
\caption{ (a) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level (b) the distance between [50 m, 30 km] is approximated by a double power-law functions (c) P($r_{g}$) at the state level (Illinois and California) (d) P($r_{g}$) for Chicago city} 
\label{fig:gyration}
\end{figure}
\FloatBarrier

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{./figures/all}
\caption{An overview of the 3D interactive web mapping interface}
\label{fig:Web_Interface}
\end{figure}
\FloatBarrier

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{./figures/Chicago}
\caption{The top 20 $\%$ movement flows around Chicago city}
\label{fig:chicago}
\end{figure}
\FloatBarrier

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{./figures/Chicago_airport}
\caption{The top 20 $\%$ movement flows between O'Hare International Airport and the city center of Chicago city}
\label{fig:Chicago_airport}
\end{figure}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{J.Y. would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
D.Z. would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
For instance, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.

Many recent studies have adopted the LBSM data streams to study human mobility patterns.
For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels), are lacking.
Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.

In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
In particular, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.

@@

\section{Mobility patterns in Location Based Social Media data}
\subsection{Geo-located Twitter data for studying large-scale user movements}
To understand detailed mobility patterns of individuals, the capability to capture human movements with fine-grained spatial and temporal granularity is critical.
In this connection, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
However, such data are often limited in spatial scale (e.g. within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.

Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with an accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
Such a dataset can cover relatively large spatial scale~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
However, due to the concerns of infringement on individual privacy, mobile phone call data are not publicly accessible at all.
Even such data were obtained in the mentioned studies, they came from various service providers covering different groups of users.
These issues limit the capability for conducting reproducible scientific findings regarding mobility research, such as validating or extending the existing discoveries.

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
A Big Data scenario emerges when millions social media users constantly posting messages.
In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy data access, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.

@@

\noindent\emph{\textbf{Definition 2. Visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.

In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
The displacement refers to an individual's re-allocation across the geographic space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
It is not equivalent to a ``trip'' took by an individual, for instance, even the time interval between two recorded locations is one month, it will still count as a displacement.
By studying the collective displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} and to quantitatively differentiate the mobility patterns from random walks~\cite{brockmann2006scaling}.
On the other hand, radius of gyration (donated as $r_{g}$) is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as fellows.
\newline

@@

\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, and therefore indicates the individual's spatial coverage, where $p_{i}$ and $p_{centroid}$ are the $ith$ location and the geometric center of the user's trajectory, respectively.
When applying the measurement to the study population, it identifies different groups of people in terms of spatial coverage from their corresponding mobility patterns. Note that both displacements and radius of gyrations are measured by ``crow's fly distance'' in this study (i.e., the direct great-circle distance between two recorded locations).
Since these metrics are based on the generated trajectories, by breaking and aggregating the trajectories in multiple spatial scales and temporal ranges, it enables performing multi-scale spatiotemporal analysis on these measurements and studying the corresponding mobility patterns.

\subsection{Multi-level spatiotemporal trajectory aggregation}
An important strategy for visual-analytics methods to deal with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers. 
To be specific, the state boundaries of the continuous United States are treated as the base layer (i.e. level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density.
In our case, the cell size for level i-1 is twice of the size in level i.
Figure~\ref{fig:multilevel} illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
Note that any predefined geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., national-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\linewidth]{./figures/multilevel}
\caption{Hierarchical spatial layers for aggregating movements in different level-of-details}
\label{fig:multilevel}
\end{figure}
\FloatBarrier

@@

In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}. 
The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
Note that different groups of Twitter users may exist in each month. 
It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}, where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/visitation}
\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors}
\label{fig:visitation}
\end{figure}
\FloatBarrier

As it is aforementioned, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
In this case, we first gathered the displacements from all the collected Twitter users in the continuous United States in year 2014, where those Twitter users with only one geo-located tweet were filtered out. 
To investigate the mobility patterns of individuals, we also derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
Note that both displacements and radius of gyrations were calculated by the direct great-circle distance ($d$) between two consecutively recorded locations in a user's trajectory.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/displacement}
\caption{(a) The probability distribution of the collective Twitter user displacements P(d) (b) the distance between [100 m, 80 km] is approximated by a double power-law functions (c) The probability distribution of the accumulated displacements of individual Twitter users P(d) (d) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months}
\label{fig:displacement}
\end{figure}
\FloatBarrier

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{./figures/gyration2}
\caption{ (a) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level (b) the distance between [50 m, 30 km] is approximated by a double power-law functions (c) P($r_{g}$) at the state level (Illinois and California) (d) P($r_{g}$) for Chicago city} 
\label{fig:gyration}
\end{figure}
\FloatBarrier

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\linewidth]{./figures/all}
\caption{An overview of the 3D interactive web mapping interface}
\label{fig:Web_Interface}
\end{figure}
\FloatBarrier

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\linewidth]{./figures/Chicago}
\caption{The top 20 $\%$ movement flows around Chicago city}
\label{fig:chicago}
\end{figure}
\FloatBarrier

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\linewidth]{./figures/Chicago_airport}
\caption{The top 20 $\%$ movement flows between O'Hare International Airport and the city center of Chicago city}
\label{fig:Chicago_airport}
\end{figure}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{
The authors would like to thank the four reviewers of IJGI for their constructive comments that better shaped the paper.
J.Y. would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
D.Z. would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}
